





\section{Project Execution Plan}


Table~\ref{tab:timeline} presents the timeline of this project. The PI has already started mentoring the PhD student who would be supported by this project. 
%The students will be ideally prepared to work on the proposed research by the project start date. 
%The PI, along with graduate (and undergraduate) students, will meet once a week. 
The PI and students will meet at least once a week.
All students will congregate and jointly develop testbeds as well as work on the implementation. 
%The PI will also participate in \ca curriculum development — both, at the graduate and undergraduate levels and \cb outreach activities  throughout the project (see Section~\ref{sec:broader}). 
The PI will also participate in curriculum development and outreach activities  throughout the project (see Section~\ref{sec:broader}).
We will disseminate our research results from this work through scientific publications at \textit{top real-time conferences} (RTSS, RTAS, ECRTS) and \textit{multidisciplinary journals} (IEEE Access, IEEE TC), technical reports, open-source releases, prototype demonstrations/videos, and outreach activities.



\input{project_description/table_timeline}
\paragraph{Plans for Assessing Success.} We will evaluate our proposed research agendas based on the successful development of analytical models, performance metrics, and scheduler implementations.  We will also track the number of citations of our publications, monitor visits to our project website, and observe the number of downloads/forks of our public code repositories. We will measure the success of our education plans by monitoring the number of student enrollment, course evaluations, ratings/comments/feedback from the students, and successful completion of course projects that turn into research publications. Our assessment of outreach activities includes \ca monitoring the number of K-12 and undergraduate student participation and \cb successful development of new pedagogical contents. We will continuously monitor and evaluate our education and outreach activities and adjust them based on the observed results. 







